
---
title: "Debug Note"
date: now
author: "Yuta & Aaron"
description: "<BR>This documents the debugging history."
title-block-banner: true
format:
  html:
    theme: 
      light: flatly
      dark: darkly    
    fontsize: 1.0em
    self-contained: true
    toc: true
    toc-location: left
    number-sections: true
    number-depth: 3
    code-fold: true
    grid:
      sidebar-width: 200px
      body-width: 1000px
      margin-width: 200px
      gutter-width: 2.5rem
execute:
  warning: false
editor: 
  markdown: 
    wrap: 72
---

## First Time Create Environment in the terminal
```{bash}
conda env create --file environment.yml
```

```{bash}
conda env list
conda init
```

close terminal and reopen

## Verify install by running the following command in the terminal
```{bash}
conda activate py39
conda list
python
```

```{python}
import os
import sys

print('getcwd:      ', os.getcwd())
sys.path.append(os.getcwd())
sys.path.append(os.getcwd()+'/src/analysis')

# from src.analysis import analysisOrbit
import analysisOrbit
from astropy import units as u

analysisRocket = analysisOrbit.hohmanTransfer(orbit_init=400, orbit_target=36000)
# analysisRocket = analysisOrbit.hohmanTransfer(orbit_init=r.initOrbit, orbit_target=r.targetOrbit, m_init=r.m_dry, I_sp=r.I_sp)
# analysisRocket = analysisOrbit.hohmanTransfer(orbit_init=400, orbit_target=35786, m_init=5000, I_sp=300)

total_delta_v = analysisRocket.calculate_delta_v()


print(f"Total delta-v: {total_delta_v}")

```

this code works!
next we verify the quarto executions.


## Using Quarto

```{r}
1+1

install.packages("reticulate")

```

```{r}
Sys.setenv(RETICULATE_PYTHON = "/opt/conda/envs/py39/bin/")
Sys.setenv(LD_LIBRARY_PATH = "/usr/lib/x86_64-linux-gnu")
Sys.setenv(R_LD_LIBRARY_PATH = "/usr/lib/x86_64-linux-gnu")

library(reticulate)
Sys.setenv(RETICULATE_PYTHON = "/opt/conda/envs/py39/bin/")
Sys.setenv(LD_LIBRARY_PATH = "/usr/lib/x86_64-linux-gnu")
Sys.setenv(R_LD_LIBRARY_PATH = "/usr/lib/x86_64-linux-gnu")

#use_condaenv("py39")

```

```{r}
R.home()
Sys.getenv("RETICULATE_PYTHON")
Sys.getenv("LD_LIBRARY_PATH")

```

```{python}
import sys

print(sys.executable)
print(sys.version)
```

```{r}
reticulate::py_config()
reticulate::use_python("/opt/conda/envs/py39/bin/python")
```
python:         /opt/conda/envs/py39/bin/python


In python interpreter,

>>> import sys
>>> 
>>> print(sys.executable)
/opt/conda/envs/py39/bin/python

```{python}
import sys

print(sys.executable)
```

```{python}
import os
import sys

print('getcwd:      ', os.getcwd())
sys.path.append(os.getcwd())
sys.path.append(os.getcwd()+'/src/analysis')

from astropy import units as u
from poliastro.bodies import Earth
from poliastro.twobody import Orbit

```

error logs

```
Traceback (most recent call last):
  File "/opt/conda/envs/py39/lib/python3.9/site-packages/llvmlite/binding/ffi.py", line 136, in __getattr__
    return self._fntab[name]
KeyError: 'LLVMPY_AddSymbol'

During handling of the above exception, another exception occurred:

Traceback (most recent call last):
  File "/opt/conda/envs/py39/lib/python3.9/site-packages/llvmlite/binding/ffi.py", line 117, in _load_lib
    self._lib_handle = ctypes.CDLL(str(lib_path))
  File "/opt/conda/envs/py39/lib/python3.9/ctypes/__init__.py", line 374, in __init__
    self._handle = _dlopen(self._name, mode)
OSError: /usr/lib/x86_64-linux-gnu/libstdc++.so.6: version `GLIBCXX_3.4.29' not found (required by /opt/conda/envs/py39/lib/python3.9/site-packages/llvmlite/binding/libllvmlite.so)

The above exception was the direct cause of the following exception:

Traceback (most recent call last):
  File "<string>", line 1, in <module>
  File "/home/vscode/R/x86_64-pc-linux-gnu-library/4.3/reticulate/python/rpytools/loader.py", line 122, in _find_and_load_hook
    return _run_hook(name, _hook)
  File "/home/vscode/R/x86_64-pc-linux-gnu-library/4.3/reticulate/python/rpytools/loader.py", line 96, in _run_hook
    module = hook()
  File "/home/vscode/R/x86_64-pc-linux-gnu-library/4.3/reticulate/python/rpytools/loader.py", line 120, in _hook
    return _find_and_load(name, import_)
  File "/opt/conda/envs/py39/lib/python3.9/site-packages/poliastro/twobody/__init__.py", line 1, in <module>
    from poliastro.twobody.orbit import Orbit
  File "/home/vscode/R/x86_64-pc-linux-gnu-library/4.3/reticulate/python/rpytools/loader.py", line 122, in _find_and_load_hook
    return _run_hook(name, _hook)
  F
```



```{r}
Sys.getenv("LD_LIBRARY_PATH")
```

```{python}
import matplotlib.pyplot as plt
# plt.ion()

# from poliastro.examples import molniya
# from poliastro.plotting import plot

# plot(molniya)
```


# For R


```r
install.packages("reactable", repos='http://cran.us.r-project.org')
install.packages("igraph")
install.packages("libmkl-rt")
install.packages("libglpk40")
install.packages("networkD3")
install.packages("reticulate")
install.packages("tidyverse")
install.packages("collapsibleTree")
install.packages("colorspace")
install.packages("jsonlite")
install.packages("DT")
install.packages("devtools")
library(devtools)

install_github("UTNAK/tansakusuR")
install_github("UTNAK/omlhashiR")
```


## Install libglpk40 package in the terminal
```{bash}
sudo apt-get update
sudo apt install -y libglpk40
```

## Install dependencies in environment.yml by running this command in the terminal
```bash
conda env update --file environment.yml --prune
```



# Troubleshooting
## Start and activate conda environment in a terminal (debugging purposes only)
```{markdown}
conda create -y -n py39 python=3.9
conda init
<!-- Close and reopen the terminal -->
conda activate py39
```



find / -name "libstdc++.so*"
```
find: ‘/etc/ssl/private’: Permission denied
/usr/lib/x86_64-linux-gnu/libstdc++.so.6
/usr/lib/x86_64-linux-gnu/libstdc++.so.6.0.28
/usr/lib/gcc/x86_64-linux-gnu/10/libstdc++.so
/usr/share/gdb/auto-load/usr/lib/x86_64-linux-gnu/libstdc++.so.6.0.28-gdb.py
```


strings /usr/lib/x86_64-linux-gnu/libstdc++.so.6 | grep GLIBCXX_3.4
strings /usr/lib/gcc/x86_64-linux-gnu/10/libstdc++.so | grep GLIBCXX_3.4

strings /opt/conda/envs/py39/lib/libstdc++.so.6 | grep GLIBCXX_3.4
strings /opt/conda/lib/libstdc++.so.6 | grep GLIBCXX_3.4



strings /usr/lib/x86_64-linux-gnu/libstdc++.so.6 | grep GLIBCXX_3.4
strings /opt/conda/envs/py39/lib/libstdc++.so.6 | grep GLIBCXX_3.4

```
(py39) (base) @UTNAK ➜ /workspaces/kepler16b-using-imce-vocabulary (feat/6-prototype-for-integration-of-orbital-analysis) $ find / -name "libstdc++.so*"
find: ‘/etc/ssl/private’: Permission denied
/usr/lib/x86_64-linux-gnu/libstdc++.so.6
/usr/lib/x86_64-linux-gnu/libstdc++.so.6.0.28
/usr/lib/gcc/x86_64-linux-gnu/10/libstdc++.so
/usr/share/gdb/auto-load/usr/lib/x86_64-linux-gnu/libstdc++.so.6.0.28-gdb.py
find: ‘/proc/tty/driver’: Permission denied
find: ‘/proc/1/task/1/fd’: Permission denied
find: ‘/proc/1/task/1/fdinfo’: Permission denied
find: ‘/proc/1/task/1/ns’: Permission denied
find: ‘/proc/1/fd’: Permission denied
find: ‘/proc/1/map_files’: Permission denied
find: ‘/proc/1/fdinfo’: Permission denied
find: ‘/proc/1/ns’: Permission denied
find: ‘/proc/115/task/115/fd’: Permission denied
find: ‘/proc/115/task/115/fdinfo’: Permission denied
find: ‘/proc/115/task/115/ns’: Permission denied
find: ‘/proc/115/fd’: Permission denied
find: ‘/proc/115/map_files’: Permission denied
find: ‘/proc/115/fdinfo’: Permission denied
find: ‘/proc/115/ns’: Permission denied
find: ‘/proc/916/task/916/fd’: Permission denied
find: ‘/proc/916/task/916/fdinfo’: Permission denied
find: ‘/proc/916/task/916/ns’: Permission denied
find: ‘/proc/916/fd’: Permission denied
find: ‘/proc/916/map_files’: Permission denied
find: ‘/proc/916/fdinfo’: Permission denied
find: ‘/proc/916/ns’: Permission denied
find: ‘/proc/26753/task/26753/fd’: Permission denied
find: ‘/proc/26753/task/26753/fdinfo’: Permission denied
find: ‘/proc/26753/task/26753/ns’: Permission denied
find: ‘/proc/26753/fd’: Permission denied
find: ‘/proc/26753/map_files’: Permission denied
find: ‘/proc/26753/fdinfo’: Permission denied
find: ‘/proc/26753/ns’: Permission denied
find: ‘/proc/27384/task/27384/fd’: Permission denied
find: ‘/proc/27384/task/27384/fdinfo’: Permission denied
find: ‘/proc/27384/task/27384/ns’: Permission denied
find: ‘/proc/27384/fd’: Permission denied
find: ‘/proc/27384/map_files’: Permission denied
find: ‘/proc/27384/fdinfo’: Permission denied
find: ‘/proc/27384/ns’: Permission denied
find: ‘/proc/42560/task/42560/fd’: Permission denied
find: ‘/proc/42560/task/42560/fdinfo’: Permission denied
find: ‘/proc/42560/task/42560/ns’: Permission denied
find: ‘/proc/42560/fd’: Permission denied
find: ‘/proc/42560/map_files’: Permission denied
find: ‘/proc/42560/fdinfo’: Permission denied
find: ‘/proc/42560/ns’: Permission denied
/opt/conda/lib/libstdc++.so
/opt/conda/lib/libstdc++.so.6
/opt/conda/lib/libstdc++.so.6.0.29
/opt/conda/envs/py39/lib/libstdc++.so.6.0.32
/opt/conda/envs/py39/lib/gcc/x86_64-conda-linux-gnu/13.2.0/libstdc++.so
/opt/conda/envs/py39/lib/libstdc++.so
/opt/conda/envs/py39/lib/libstdc++.so.6
/opt/conda/envs/py39/x86_64-conda-linux-gnu/lib/libstdc++.so.6.0.32
/opt/conda/envs/py39/x86_64-conda-linux-gnu/lib/libstdc++.so
/opt/conda/envs/py39/x86_64-conda-linux-gnu/lib/libstdc++.so.6
/opt/conda/pkgs/libstdcxx-ng-13.2.0-hc0a3c3a_7/lib/libstdc++.so.6.0.32
/opt/conda/pkgs/libstdcxx-ng-13.2.0-hc0a3c3a_7/lib/libstdc++.so
/opt/conda/pkgs/libstdcxx-ng-13.2.0-hc0a3c3a_7/lib/libstdc++.so.6
/opt/conda/pkgs/libstdcxx-devel_linux-64-13.2.0-hceb6213_107/lib/gcc/x86_64-conda-linux-gnu/13.2.0/libstdc++.so
/opt/conda/pkgs/libstdcxx-devel_linux-64-13.2.0-hceb6213_107/x86_64-conda-linux-gnu/lib/libstdc++.so.6.0.32
/opt/conda/pkgs/libstdcxx-devel_linux-64-13.2.0-hceb6213_107/x86_64-conda-linux-gnu/lib/libstdc++.so
/opt/conda/pkgs/libstdcxx-devel_linux-64-13.2.0-hceb6213_107/x86_64-conda-linux-gnu/lib/libstdc++.so.6
find: ‘/var/lib/apt/lists/partial’: Permission denied
find: ‘/var/cache/ldconfig’: Permission denied
find: ‘/var/cache/apt/archives/partial’: Permission denied
find: ‘/root’: Permission denied
/workspaces/.codespaces/shared/editors/jetbrains/pycharm-2023.1.1/plugins/remote-dev-server/selfcontained/lib/libstdc++.so.6
/workspaces/.codespaces/shared/editors/jetbrains/JetBrainsRider-2023.1/plugins/remote-dev-server/selfcontained/lib/libstdc++.so.6
/workspaces/.codespaces/shared/editors/jetbrains/RubyMine-2023.1.1/plugins/remote-dev-server/selfcontained/lib/libstdc++.so.6
/workspaces/.codespaces/shared/editors/jetbrains/idea-IU-231.8770.65/plugins/remote-dev-server/selfcontained/lib/libstdc++.so.6
(py39) (base) @UTNAK ➜ /workspaces/kepler16b-using-imce-vocabulary (feat/6-prototype-for-integration-of-orbital-analysis) $ 
(py39) (base) @UTNAK ➜ /workspaces/kepler16b-using-imce-vocabulary (feat/6-prototype-for-integration-of-orbital-analysis) $ 
(py39) (base) @UTNAK ➜ /workspaces/kepler16b-using-imce-vocabulary (feat/6-prototype-for-integration-of-orbital-analysis) $ strings /opt/conda/envs/py39/lib/libstdc++.so.6 | grep GLIBCXX_3.4
GLIBCXX_3.4
GLIBCXX_3.4.1
GLIBCXX_3.4.2
GLIBCXX_3.4.3
GLIBCXX_3.4.4
GLIBCXX_3.4.5
GLIBCXX_3.4.6
GLIBCXX_3.4.7
GLIBCXX_3.4.8
GLIBCXX_3.4.9
GLIBCXX_3.4.10
GLIBCXX_3.4.11
GLIBCXX_3.4.12
GLIBCXX_3.4.13
GLIBCXX_3.4.14
GLIBCXX_3.4.15
GLIBCXX_3.4.16
GLIBCXX_3.4.17
GLIBCXX_3.4.18
GLIBCXX_3.4.19
GLIBCXX_3.4.20
GLIBCXX_3.4.21
GLIBCXX_3.4.22
GLIBCXX_3.4.23
GLIBCXX_3.4.24
GLIBCXX_3.4.25
GLIBCXX_3.4.26
GLIBCXX_3.4.27
GLIBCXX_3.4.28
GLIBCXX_3.4.29
GLIBCXX_3.4.30
GLIBCXX_3.4.31
GLIBCXX_3.4.32
_ZNKSt14basic_ifstreamIcSt11char_traitsIcEE7is_openEv@GLIBCXX_3.4
_ZNSt13basic_istreamIwSt11char_traitsIwEE6ignoreEv@@GLIBCXX_3.4.5
_ZNKSbIwSt11char_traitsIwESaIwEE11_M_disjunctEPKw@GLIBCXX_3.4
_ZNKSt14basic_ifstreamIwSt11char_traitsIwEE7is_openEv@@GLIBCXX_3.4.5
GLIBCXX_3.4.21
GLIBCXX_3.4.9
_ZSt10adopt_lock@@GLIBCXX_3.4.11
GLIBCXX_3.4.10
GLIBCXX_3.4.16
GLIBCXX_3.4.32
GLIBCXX_3.4.1
_ZNSt19istreambuf_iteratorIcSt11char_traitsIcEEppEv@GLIBCXX_3.4
GLIBCXX_3.4.28
_ZNSs7_M_copyEPcPKcm@GLIBCXX_3.4
GLIBCXX_3.4.25
_ZNSt19istreambuf_iteratorIcSt11char_traitsIcEEppEv@@GLIBCXX_3.4.5
_ZNSs7_M_moveEPcPKcm@@GLIBCXX_3.4.5
_ZNKSt13basic_fstreamIwSt11char_traitsIwEE7is_openEv@GLIBCXX_3.4
_ZNKSt13basic_fstreamIcSt11char_traitsIcEE7is_openEv@GLIBCXX_3.4
_ZNSbIwSt11char_traitsIwESaIwEE4_Rep26_M_set_length_and_sharableEm@@GLIBCXX_3.4.5
_ZNSs4_Rep26_M_set_length_and_sharableEm@GLIBCXX_3.4
_ZSt10defer_lock@@GLIBCXX_3.4.11
_ZN10__gnu_norm15_List_node_base4swapERS0_S1_@@GLIBCXX_3.4
_ZNSs9_M_assignEPcmc@@GLIBCXX_3.4.5
_ZNKSbIwSt11char_traitsIwESaIwEE15_M_check_lengthEmmPKc@@GLIBCXX_3.4.5
_ZNKSt14basic_ifstreamIcSt11char_traitsIcEE7is_openEv@@GLIBCXX_3.4.5
_ZNSbIwSt11char_traitsIwESaIwEE7_M_moveEPwPKwm@GLIBCXX_3.4
GLIBCXX_3.4.24
_ZNVSt9__atomic011atomic_flag12test_and_setESt12memory_order@@GLIBCXX_3.4.11
GLIBCXX_3.4.20
_ZNSt11char_traitsIwE2eqERKwS2_@@GLIBCXX_3.4.5
GLIBCXX_3.4.12
_ZNSi6ignoreEv@@GLIBCXX_3.4.5
GLIBCXX_3.4.2
_ZNSt11char_traitsIcE2eqERKcS2_@@GLIBCXX_3.4.5
GLIBCXX_3.4.6
_ZNSt18condition_variable4waitERSt11unique_lockISt5mutexE@GLIBCXX_3.4.11
GLIBCXX_3.4.15
GLIBCXX_3.4.31
_ZNKSt13basic_fstreamIcSt11char_traitsIcEE7is_openEv@@GLIBCXX_3.4.5
_ZNSs9_M_assignEPcmc@GLIBCXX_3.4
GLIBCXX_3.4.19
_ZNKSt14basic_ofstreamIwSt11char_traitsIwEE7is_openEv@GLIBCXX_3.4
_ZNSt19istreambuf_iteratorIwSt11char_traitsIwEEppEv@GLIBCXX_3.4
GLIBCXX_3.4.27
_ZN10__gnu_norm15_List_node_base7reverseEv@@GLIBCXX_3.4
_ZN10__gnu_norm15_List_node_base4hookEPS0_@@GLIBCXX_3.4
_ZNSt11char_traitsIwE2eqERKwS2_@GLIBCXX_3.4
_ZNSbIwSt11char_traitsIwESaIwEE7_M_copyEPwPKwm@GLIBCXX_3.4
_ZNSbIwSt11char_traitsIwESaIwEE7_M_copyEPwPKwm@@GLIBCXX_3.4.5
GLIBCXX_3.4.23
GLIBCXX_3.4.3
GLIBCXX_3.4.7
_ZNSi6ignoreEl@@GLIBCXX_3.4.5
_ZNKSbIwSt11char_traitsIwESaIwEE11_M_disjunctEPKw@@GLIBCXX_3.4.5
_ZNSt13basic_istreamIwSt11char_traitsIwEE6ignoreEv@GLIBCXX_3.4
_ZNKSt13basic_fstreamIwSt11char_traitsIwEE7is_openEv@@GLIBCXX_3.4.5
_ZNSbIwSt11char_traitsIwESaIwEE7_M_moveEPwPKwm@@GLIBCXX_3.4.5
GLIBCXX_3.4.18
_ZNSbIwSt11char_traitsIwESaIwEE4_Rep26_M_set_length_and_sharableEm@GLIBCXX_3.4
GLIBCXX_3.4.30
_ZNSt13basic_istreamIwSt11char_traitsIwEE6ignoreEl@@GLIBCXX_3.4.5
_ZSt15future_category@@GLIBCXX_3.4.14
_ZNSi6ignoreEl@GLIBCXX_3.4
GLIBCXX_3.4.29
_ZNSt11char_traitsIcE2eqERKcS2_@GLIBCXX_3.4
_ZNKSs15_M_check_lengthEmmPKc@GLIBCXX_3.4
_ZN10__gnu_norm15_List_node_base8transferEPS0_S1_@@GLIBCXX_3.4
_ZNSbIwSt11char_traitsIwESaIwEE9_M_assignEPwmw@GLIBCXX_3.4
_ZNVSt9__atomic011atomic_flag5clearESt12memory_order@@GLIBCXX_3.4.11
_ZNKSt14basic_ofstreamIcSt11char_traitsIcEE7is_openEv@@GLIBCXX_3.4.5
_ZNKSt14basic_ofstreamIcSt11char_traitsIcEE7is_openEv@GLIBCXX_3.4
_ZNSs7_M_moveEPcPKcm@GLIBCXX_3.4
_ZNSt13basic_istreamIwSt11char_traitsIwEE6ignoreEl@GLIBCXX_3.4
_ZNSbIwSt11char_traitsIwESaIwEE9_M_assignEPwmw@@GLIBCXX_3.4.5
_ZNKSbIwSt11char_traitsIwESaIwEE15_M_check_lengthEmmPKc@GLIBCXX_3.4
_ZNKSs11_M_disjunctEPKc@@GLIBCXX_3.4.5
_ZN10__gnu_norm15_List_node_base6unhookEv@@GLIBCXX_3.4
GLIBCXX_3.4.22
_ZNSt19istreambuf_iteratorIwSt11char_traitsIwEEppEv@@GLIBCXX_3.4.5
_ZNSi6ignoreEv@GLIBCXX_3.4
_ZNSs7_M_copyEPcPKcm@@GLIBCXX_3.4.5
GLIBCXX_3.4.8
GLIBCXX_3.4.13
_ZSt11try_to_lock@@GLIBCXX_3.4.11
_ZNKSt14basic_ofstreamIwSt11char_traitsIwEE7is_openEv@@GLIBCXX_3.4.5
GLIBCXX_3.4.17
GLIBCXX_3.4.4
_ZNKSs15_M_check_lengthEmmPKc@@GLIBCXX_3.4.5
_ZNKSt14basic_ifstreamIwSt11char_traitsIwEE7is_openEv@GLIBCXX_3.4
_ZNSs4_Rep26_M_set_length_and_sharableEm@@GLIBCXX_3.4.5
GLIBCXX_3.4.26
_ZNKSs11_M_disjunctEPKc@GLIBCXX_3.4
(py39) (base) @UTNAK ➜ /workspaces/kepler16b-using-imce-vocabulary (feat/6-prototype-for-integration-of-orbital-analysis) $ 
```


```{r}
Sys.setenv(LD_LIBRARY_PATH = "/opt/conda/envs/py39/lib/")
Sys.setenv(R_LD_LIBRARY_PATH = "/opt/conda/envs/py39/lib/")

library(reticulate)



```


```{r}
use_condaenv("py39")

R.home()
Sys.getenv("RETICULATE_PYTHON")
Sys.getenv("LD_LIBRARY_PATH")

```

```{python}
import sys

print(sys.executable)
print(sys.version)
```

```{python}
import os
import sys

print('getcwd:      ', os.getcwd())
sys.path.append(os.getcwd())
sys.path.append(os.getcwd()+'/src/analysis')

from astropy import units as u
from poliastro.bodies import Earth
from poliastro.twobody import Orbit

```




 export LD_LIBRARY_PATH="/opt/conda/lib/:$LD_LIBRARY_PATH"

cd /opt/conda/envs/py39/lib/
sudo cp libstdc++.so.6 /usr/lib/x86_64-linux-gnu/libstdc++.so.6
strings /usr/lib/x86_64-linux-gnu/libstdc++.so.6 | grep GLIBCXX_3.4
strings /opt/conda/envs/py39/lib/libstdc++.so.6 | grep GLIBCXX_3.4


 ```{r}
Sys.setenv(LD_LIBRARY_PATH = "/opt/conda/lib/")

library(reticulate)
use_condaenv("py39")

 ```

 ```{r}
 Sys.getenv("LD_LIBRARY_PATH")

 ```
 ```{r}
Sys.getenv("LD_LIBRARY_PATH")
Sys.setenv(LD_LIBRARY_PATH = "/opt/conda/lib/")

 ```


 ```{r}
 Sys.getenv("LD_LIBRARY_PATH")

 ```



```{python}
import os
import sys

print('getcwd:      ', os.getcwd())
sys.path.append(os.getcwd())
sys.path.append(os.getcwd()+'/src/analysis')

from astropy import units as u
from poliastro.bodies import Earth
from poliastro.twobody import Orbit

```


